### 2023-11-23 main.tex
^-^
^_^

\section{Duality}\label{sectionDuality}
In this section we prove the first main result of this paper. We show that the multispecies stirring process with open boundary
can be studied by means of a dual process. After recalling the definition of duality between two
Markov processes in Section \ref{def-duality}, we formulate our duality result  in Theorem \ref{thm-duality}. A proof of the theorem is given in Section \ref{proof-th-duality}.
The duality result is important since it yields several simplifications, the main one being that the
dual process has absorbing sites. Therefore, as shown in Corollary \ref{prop-absorbing}, the study of correlations in the non-equilibrium steady state of the multispecies stirring process with open boundary
is reduced to the study of the absorption probabilities of dual particles.

@@

%\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N}^{u(x)}|(A^{+})_{a}^{u(x)}=0

@@

\label{prop-absorbing}

@@

\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}+\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)(-1)\left\{\sum_{q_{1}=1}^{L}\delta_{\tau_{q_{1}},N}\sum_{a_{q_{1}}=1}^{N-1}\mathbbm{1}_{\{\sigma_{q_{1}}=a_{q_{1}}\}}\right\}+\nonumber\\

@@

@@

	&\mathbb{E}_{\mu}\left[\left(\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}-\langle\rho_{a_{1}}^{x_{1}}\rangle \right)\left(\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}-\langle\rho_{a_{2}}^{x_{2}}\rangle \right)\left(\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}-\langle\rho_{a_{3}}^{x_{3}}\rangle \right)\right]\nonumber\\

@@

	\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=1\}}\right]=\sum_{q=0}^{m}(\alpha-\beta)^{q}\beta^{m-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq m}\prod_{k=1}^{q}\frac{\left(L+1-x_{\ell_{k}}-q+k\right)}{(2+L-k)}\dt

@@

	\item \textit{Arbitrary correlations}: exploiting duality, the steady state correlations can be expressed in terms of absorption probabilities of the dual particles. These probability are hard to find in this partial exclusion situation, however correlation can be formally written. Section \ref{Subsection-ss-nonI}.

@@

Therefore, up to this constant, $\mathbb{E}_{\mu}\left[D(\bm{n},\bm{\xi})\right]$ gives the non-equilibrium steady state $m-$points correlations. The following equalities hold using duality relation \eqref{duality-expectation}:

@@

		\frac{\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}n_{a_{k}}^{x_{k}}\right]}{C(\nu,m)}&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\xi})\right]=\lim_{t\to\infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\xi}(t))\right]

@@

			\mathbb{E}_{\mu}\left[n_{a}^{x}\right]&=\nu\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{a}^{x})\right]\\&=\nu\sum_{t_{a}=0}^{1}\left(\rho_{a}^{L}\right)^{t_{s}}\left(\rho_{s}^{R}\right)^{1-t_{s}}\mathbb{P}_{\delta_{a}^{x}}\left(\xi_{\infty}=t_{a}\delta_{0}+(1-t_{a})\delta_{L+1}\right)\dt

@@

	\mathbb{E}_{\mu}\left[n_{a}^{x}\right]=\nu\frac{\alpha_{a}(L|\beta|-|\beta|x+1)+\beta_{a}(|\alpha|x+1-|\alpha|)}{|\alpha||\beta|L-|\alpha||\beta|+|\alpha|+|\beta|}\dt

@@

		\mathbb{E}_{\mu}\left[n_{a}^{x}\right]=\frac{\alpha_{a}(L-x+1)+\beta_{a}x}{L+1}

>>>>

\section{Duality}\label{sectionDuality}
In this section we prove the first main result of this paper. We show that the multispecies stirring process with open boundary
can be studied by means of a dual process. After recalling the definition of duality between two
Markov processes in Section \ref{def-duality}, we formulate our duality result  in Theorem \ref{thm-duality}. A proof of the theorem is given in Section \ref{proof-th-duality}.
The duality result is important since it yields several simplifications, the main one being that the
dual process has absorbing sites. Therefore, as shown in Corollary \ref{Corolollary-ABS_Corr-abstract}, the study of correlations in the non-equilibrium steady state of the multispecies stirring process with open boundary
is reduced to the study of the absorption probabilities of dual particles.

@@

%\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N}^{u(x)}|($\mathbf{a}$^{+})_{a}^{u(x)}=0

@@

@@

\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}+\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)(-1)\left\{\sum_{q_{1}=1}^{L}\delta_{\tau_{q_{1}},N}\sum_{a_{q_{1}}=1}^{N-1}\mathbbm{1}_{\{Y_{q_{1}}=a_{q_{1}}\}}\right\}+\nonumber\\

@@

\begin{remark}\label{Remark-extension-graph-nu}

@@

	&\mathbb{E}\left[\left(\mathbbm{1}_{\{Y_{x_{1}}=a_{1}\}}-\langle\rho_{a_{1}}^{x_{1}}\rangle \right)\left(\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}-\langle\rho_{a_{2}}^{x_{2}}\rangle \right)\left(\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}-\langle\rho_{a_{3}}^{x_{3}}\rangle \right)\right]\nonumber\\

@@

	\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=1\}}\right]=\sum_{q=0}^{m}(\alpha-\beta)^{q}\beta^{m-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq m}\prod_{k=1}^{q}\frac{\left(L+1-x_{\ell_{k}}-q+k\right)}{(2+L-k)}\dt

@@

	\item \textit{Arbitrary correlations}: exploiting duality, the steady state correlations can be expressed in terms of absorption probabilities of the dual particles. These probability are hard to find in this partial exclusion situation, however correlation can be formally written. Section \ref{Subsection-ss-nonI}. \textbf{[Do we need this or it is enough Remark \ref{Remark-extension-graph-nu}?]}

@@

Therefore, up to this constant, $\mathbb{E}\left[D(\bm{n},\bm{\xi})\right]$ gives the non-equilibrium steady state $m-$points correlations. The following equalities hold using duality relation \eqref{duality-expectation}:

@@

		\frac{\mathbb{E}\left[\prod_{k=1}^{m}n_{a_{k}}^{x_{k}}\right]}{C(\nu,m)}&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\xi})\right]=\lim_{t\to\infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\xi}(t))\right]

@@

			\mathbb{E}\left[n_{a}^{x}\right]&=\nu\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{a}^{x})\right]\\&=\nu\sum_{t_{a}=0}^{1}\left(\rho_{a}^{L}\right)^{t_{s}}\left(\rho_{s}^{R}\right)^{1-t_{s}}\mathbb{P}_{\delta_{a}^{x}}\left(\xi_{\infty}=t_{a}\delta_{0}+(1-t_{a})\delta_{L+1}\right)\dt

@@

	\mathbb{E}\left[n_{a}^{x}\right]=\nu\frac{\alpha_{a}(L|\beta|-|\beta|x+1)+\beta_{a}(|\alpha|x+1-|\alpha|)}{|\alpha||\beta|L-|\alpha||\beta|+|\alpha|+|\beta|}\dt

@@

		\mathbb{E}\left[n_{a}^{x}\right]=\frac{\alpha_{a}(L-x+1)+\beta_{a}x}{L+1}
